Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-03-02 papers/CADE19/paper.tex
fixed comparative section

After covering relevant background material in Section~\ref{sec:background} the remainder of the paper makes two main contributions.
Firstly, in Section~\ref{sec:awr:study} we experimentally confirm the folklore that (i) the choice of age/weight ratio often has a significant effect on the performance of proof search, and (ii) there is no `best' age/weight ratio: indeed, a large range of pragmatically useful ratios exists.
Secondly, we demonstrate (Section~\ref{sec:varying:study}) that varying the age-weight ratio over time can achieve better performance than a fixed ratio and use this to motivate the addition of so-called \emph{age/weight shapes} for varying the ratio over time.
Experiments (Section~\ref{sec:experiments}) with these new options implemented in the Vampire theorem prover show a significant improvement, proving many new problems unsolvable by any current configuration of Vampire as well as other competitive solvers.

@@

%\subsection{New Problems}
Finally, two problems were solved which were marked with an ``Unknown'' status in the TPTP headers.
Only converging with frequency 50 solved \texttt{SET345-6} and only decaying with frequency 1 solved \texttt{LAT320+3}.

%\clearpage

\iffalse
%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with other Solvers}

\begin{table}[t]
\caption{Total number of problems solved compared to other solvers.\label{tab:other}}
\centering
\begin{tabular}{l|l|l}
Solver 		& Total solved & Uniquely solved \\ \hline
Vampire (old)	& 13,057 & \\
Vampire (new)   & 13,191 & \\
E 			& \\
iProver		& \\
CVC4		& \\
\end{tabular}
\end{table}

To place these results in context, we compare the overall number of problems solved by our new strategies with the results of other solvers (using their previous CASC competition strategy). These results are from 300s and are given in Table~\ref{tab:other}. 
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\label{sec:conclusions}

>>>>

After covering relevant background material in Section~\ref{sec:background} the remainder of the paper makes two main contributions.
Firstly, in Section~\ref{sec:awr:study} we experimentally confirm the folklore that (i) the choice of age/weight ratio often has a significant effect on the performance of proof search, and (ii) there is no `best' age/weight ratio: indeed, a large range of pragmatically useful ratios exists.
Secondly, we demonstrate (Section~\ref{sec:varying:study}) that varying the age-weight ratio over time can achieve better performance than a fixed ratio and use this to motivate the addition of so-called \emph{age/weight shapes} for varying the ratio over time.
Experiments (Section~\ref{sec:experiments}) with these new options implemented in the Vampire theorem prover show a significant improvement, proving many new problems unsolvable by any current configuration of Vampire.

@@

Finally, two problems were solved which were marked with an ``Unknown'' status in the TPTP headers.
Only converging with frequency 50 solved \texttt{SET345-6} and only decaying with frequency 1 solved \texttt{LAT320+3}.

\section{Conclusions and Future Work}
\label{sec:conclusions}
